### 2019-03-31 Paper/Paper.tex
Write paper through results (bullet points)

\subsection{Solution Times}
\hyperlink{Table 2}{Table 2} reports the solution times for the Richter et al. (2013) and Gust et al. (2017) solution methods for the models with and without capital. %Say something about the solution times% %Say something about the machine the solution times were computed on

\begin{table}[H]
  \centering
  \hypertarget{Table 2}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c c c}
    \hline
    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
    & Iterations & Total Time & Iterations & Total time\\
    \hline
  Richter et al. (2013) & 67 & 17.9s & 65 & 0h 15m 37.1s\\    
  Gust et al. (2017) & 66 & 46s & 1170 &  5h 32m 48.6s\\
  \hline
\end{tabular}
  \caption{Solution times}
  \label{Tab:2}
\end{table}

\subsection{Policy Functions}

\subsection{Euler Equation Errors}

@@

>>>>

\subsection{Solution Times}
\hyperlink{Table 2}{Table 2} reports the solution times for the Richter et al. (2013) and Gust et al. (2017) solution methods for the models with and without capital. The solution times were computed with multi-core processing using the Parallel Computing Toolbox and integrate Fortran in the interpolation steps of our algorithm through MATLAB executable functions. The solution times represent one run of each algorithm. The machine used to compute solution times has two CPUs (at 2.30GHz), each with 16 cores. %Say something about the solution times%
\begin{itemize}
\item Gust et al. method slower, particularly on the model with capital. The differential blows up for the model with capital.
\item The speed and speed differential is influenced by the parameterization, and appears to take more time on the boundary of convergence for each algorithm.
\end{itemize}
\begin{table}[H]
  \centering
  \hypertarget{Table 2}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c c c}
    \hline
    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
    & Iterations & Total Time & Iterations & Total time\\
    \hline
  Richter et al. (2013) & 67 & 17.9s & 65 & 0h 15m 37.1s\\    
  Gust et al. (2017) & 66 & 46s & 1170 &  5h 32m 48.6s\\
  \hline
\end{tabular}
  \caption{Solution times}
\end{table}

\subsection{Policy Functions} \hyperlink{Figure 1}{Figure 1} shows the cross-section of the labor policy functions with the interest rate and risk premium for the model with capital. \hyperlink{Table 3}{Table 3} reports the RMSE and mean \% error from linear policy functions. The corresponding results for the model without capital is reported in \hyperlink{Appendix C}{Appendix C}.

\begin{itemize}
\item ART is visually a lot smoother; matched with statistics
  \item the Gust Et Al combined policy function si very similar to the non-ZLB policy function. All Gust Et Al policy functions have a kink corresponding to the ZLB. 
  \item Percent error and RMSE error wise though, this is not too big of a difference?
    \item say something about what the mean \% error and RMSE is
  \end{itemize}

\begin{figure}[H]
\hypertarget{Figure 1}  
    \centering
    \includegraphics[scale=.6]{pfs3D_CAPITAL-eps-converted-to.pdf}%{pfs3D_CAPITAL.eps}
  \caption{Labor policy function for model with capital}    
  \label{Fig:1}
  \end{figure}

\begin{table}[H]
  \centering
  \hypertarget{Table 3}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c c c}
    \hline
    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
    & Mean \% Error & RMSE & Mean \% Error & RMSE\\
    \hline
    Richter et al. policy & 0.46545\% &0.0020137 consumption units & 0.19585\% & .0029035 labor units \\    
  Gust et al. policy & 0.45556\% & 0.0019792 consumption units & 0.56142\% & 0.0076665 labor units \\
  \hline
\end{tabular}
  \caption{Smoothness measures for labor policy functions ($c$ for model with capital and $n$ for model with capital). Gust et al. combined policy functions are reported.}
\end{table}

\subsection{Euler Equation Errors} \hyperlink{Figure 2}{Figure 2} shows the distribution of the absolute value of the Euler equation errors in base 10 logarithms for the household FOC bond, FOC capital, FOC investment, and price Phillips curve in the model with capital. We also report the mean and maximum error. The corresponding results for the model without capital is reported in \hyperlink{Appendix C}{Appendix C}.

\begin{itemize}
\item Euler equations very comparable between algorithms
\item Gust et al does slightly worse. Means are similar but max is higher.
  \end{itemize}

\begin{figure}[H]
\hypertarget{Figure 2}  
    \centering
    \includegraphics[scale=1.5]{eeerrors_C.eps}%{pfs3D_CAPITAL.eps}
  \caption{Euler equation errors for model with capital}    
  \end{figure}

@@

\section{Results for model without capital} \hypertarget{Appendix C}
The following reports the corresponding results for the model wtihout capital. \hyperlink{Figure 3}{Figure 3} shows the cross-section of the consumption policy functions with the interest rate and risk premium. \hyperlink{Figure 4}{Figure 4} shows the distribution of the absolute value of the Euler equation errors in base 10 logarithms for the consumption euler Equation and the price Phillips curve.

\begin{figure}[H]
\hypertarget{Figure 3}  
    \centering
    \includegraphics[scale=.6]{pfs3D.eps}
  \caption{Consumption policy function for model without capital}    
  \end{figure}

\begin{itemize}
\item Smoother in general
\item Very close between ART and GustEtAl
  \end{itemize}

\begin{figure}[H]
\hypertarget{Figure 4}  
    \centering
    \includegraphics[scale=1.5]{eeerrors.eps}
  \caption{Euler equation errors for model without capital}    
  \end{figure}

\begin{itemize}
\item Bimodality more distinct in Gust et al policy functions
\item Very similar with regards to mean and max; Gust et al does slightly better in consumption Euler
\end{itemize}
